Last glacial cycle glacier erosion potential in the Alps

### 2021-02-03 articles/erosion/alps-erosion.tex
Change to Copernicus ESurf latex class.
Add author contrib, acknowledgements etc.

\documentclass[utf8]{article}

% default packages
\usepackage{doi}
\usepackage{authblk}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{xcolor}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear,round]{natbib}
%\usepackage{CJK}  % texlive-langjapanese

% review mode
\usepackage{geometry}
\usepackage{lineno}
\linenumbers
\linespread{1.5}

% custom colours
\definecolor{darkblue}{cmyk}{0.9,0.3,0.0,0.0}
\definecolor{darkgreen}{cmyk}{0.8,0.0,1.0,0.0}
\definecolor{darkred}{cmyk}{0.1,0.9,0.8,0.0}
\definecolor{darkorange}{cmyk}{0.0,0.5,1.0,0.0}
\definecolor{darkpurple}{cmyk}{0.6,0.7,0.0,0.0}
\definecolor{darkbrown}{cmyk}{0.23,0.73,0.98,0.12}

% custom commands
\newcommand{\idea}[1]{\textcolor{darkgreen}{\emph{[\textbf{IDEA:} #1]}}}
\newcommand{\note}[1]{\textcolor{darkblue}{\emph{[\textbf{NOTE:} #1]}}}
\newcommand{\todo}[1]{\textcolor{darkred}{\emph{[\textbf{TODO:} #1]}}}
\newcommand{\aref}[0]{\textcolor{darkblue}{\textbf{[REF.]}}}
\newcommand{\ian}[1]{\textcolor{darkbrown}{\emph{[\textbf{IAN:} #1]}}}

@@

% document properties
\title{Last glacial cycle glacier erosion potential in the Alps}
\author[1]{Julien Seguinot}
\author[2]{Ian Delaney}
\affil[1]{Anafi, Greece}
\affil[2]{Institute of Earth Surface Dynamics, University of Lausanne, Switzerland}

@@

% ----------------------------------------------------------------------
\section{Introduction}
% ----------------------------------------------------------------------

@@

%\paragraph{Acknowledgements}
%\paragraph{Author contributions}
%\paragraph{Conflict of interest}
%\paragraph{Contribution to the field}
%\paragraph{Data availability}

@@

\bibliographystyle{abbrvnat}
\bibliography{../../../references/references}

>>>>

\documentclass[esurf, manuscript]{copernicus}

% custom colours (colorbrewer2.org)
\definecolor{Bu}{cmyk}{1.00,0.45,0.00,0.07}  % Blues
\definecolor{Gn}{cmyk}{1.00,0.20,1.00,0.00}  % Greens
\definecolor{Rd}{cmyk}{0.35,0.95,0.85,0.00}  % Reds
\definecolor{Or}{cmyk}{0.35,0.75,1.00,0.00}  % Oranges
\definecolor{Pu}{cmyk}{0.70,0.80,0.00,0.00}  % Purples
\definecolor{Br}{cmyk}{0.40,0.75,1.00,0.00}  % YlOrBr

% custom commands (remove before submission)
\newcommand{\note}[1]{\textcolor{Or}{\emph{[\textbf{NOTE:} #1]}}}
\newcommand{\todo}[1]{\textcolor{Rd}{\emph{[\textbf{TODO:} #1]}}}
\newcommand{\aref}[0]{\textcolor{Rd}{\textbf{[REF.]}}}
\newcommand{\ian}[1]{\textcolor{Or}{\emph{[\textbf{IAN:} #1]}}}

% color links (remove before submission)
\hypersetup{colorlinks, citecolor=Bu, linkcolor=Bu, urlcolor=Bu}

@@

% document properties
\title{Last glacial cycle glacier erosion potential in the Alps}
\Author[1]{Julien}{Seguinot}
\Author[2]{Ian}{Delaney}
\affil[1]{Anafi, Greece}
\affil[2]{Institute of Earth Surface Dynamics, University of Lausanne, Switzerland}
\runningtitle{Last glacial cycle glacier erosion potential in the Alps}
\runningauthor{J.~Seguinot and I.~Delanay}

@@

% ----------------------------------------------------------------------
\introduction
% ----------------------------------------------------------------------

@@

\codedataavailability{%
    PISM is available as open-source software (http://pism-docs.org).
    Time and domain-aggregated erosion variables such as used in the figures is
    available for the four presented erosion power-laws
    (\doi{10.5281/zenodo.4495419}). Other model output variables were
    previously made available (\doi{10.5281/zenodo.1423160},
    \doi{10.5281/zenodo.1423176}).}

\videosupplement{
    A supplementary animation is available
    (\url{https://vimeo.com/503162771}).}

\authorcontribution{%
    J.~Seguinot performed the computations and initially drafted the
    manuscript. I.~Delanay contributed to interpret the results in broader
    context.}

\competinginterests{%
    The authors declare that they have no conflict of interest.}

\begin{acknowledgements}
    We are very thankful to Constantine Khroulev, Ed Bueler, and Andy
    Aschwanden for their constant help and development with PISM, without whom
    this work would not have been possible. J.~Seguinot would like to thank
    John Jansen and Martin Margold for insightful early discussions, Susan
    Ivy-Ochs for being a constant (droid) motivator, as well as Popi, Karsta
    and Stefan for welcoming him on Anafi and providing agreeable conditions
    for work in times of pandemic.
    J.~Seguinot exclusively used gear transported on a bike for 5000\,km across
    Europe and fourteen countries (except for new underwear).
    The (previously published) ice flow simulations were made with computer
    resources provided by the Swiss National Supercomputing Centre (CSCS)
    allocations no.~s573 and sm13 to J.~Seguinot.
\end{acknowledgements}

@@

\bibliographystyle{copernicus}
\bibliography{../../../references/references}
